An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-03 EconGrowth-R-Functions.Rnw
Now including several mods to the presentation based on feedback from Caleb and Lucas.

#################
# Creates a plot with y residuals vs. energy (e). The y residuals are from a Cobb-Douglas model without energy.
# The energy term on the x axis is whatever type is specified in the calling funciton
partialResidualPlot <- function(countryAbbrev, energyType, textScaling=1.0){
  # Get the model
  cdModel <- cdModel(countryAbbrev)
  # Get the residuals
  cdResid <- resid(cdModel)
  cdResid <- data.frame(cdResid)
  cdResid <- padRows(countryAbbrev=countryAbbrev, df=cdResid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, cdResid)
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  plot <- xyplot(cdResid ~ iEToFit, data=data,
                 type=c('p','smooth'),
                 col="black",
                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
                 ylab=list(label="$y$ residuals", cex=textScaling)
                 )
  return(plot)  
}
@

>>>>

#################
# Creates a plot with y residuals vs. energy (e). The y residuals are from a Cobb-Douglas model without energy.
# The energy term on the x axis is whatever type is specified in the calling funciton
partialResidualPlot <- function(countryAbbrev, energyType, textScaling=1.0){
  # Get the model
  cdModel <- cdModel(countryAbbrev)
  # Get the residuals
  cdResid <- resid(cdModel)
  cdResid <- data.frame(cdResid)
  cdResid <- padRows(countryAbbrev=countryAbbrev, df=cdResid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, cdResid)
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  plot <- xyplot(cdResid ~ iEToFit, data=data,
#                 type=c("p",:smooth"),
                 type=c("p"),
                 col="black",
                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
                 )
  return(plot)  
}
@
